### 2020-03-29 papers.tex
papers.tex: Add missing file reference to latecomer paper 11
Add reviews arriving during the preceding proceedings weekend
Add late, very late, so extremely late paper from last year
Add papers and a review arriving roughly by the actual final paper deadline

@@

% TODO
\addreview{SIGBOVIK_2020_review_3}{0cm}
\addreview{SIGBOVIK_2020_review_4}{0cm}
\addreview{SIGBOVIK_2020_review_6}{0cm}

>>>>

	{Deep industrial espionage}
	{Samuel Albanie, James Thewlis, Sebastien Ehrhardt, Jo\~ao F.\@ Henriques}
	{Keywords: late, very late, so extremely late}
	{SIGBOVIK_2019_paper_43}

@@

	{The SIGBOVIK 2020 field guide to plants}
	{Jim McCann (editor)}
	{Keywords: field guide, plants, to}
	{SIGBOVIK_2020_paper_31}
	{SIGBOVIK '75 technical note: Conditional move for shell script acceleration}
	{Dr.\@ James McCann, Dr.\@ Tom Murphy VII}
	{Keywords: cond-, itional, move}
	{SIGBOVIK_2020_paper_32}
	{Ntinuation copassing style}
	{Cameron Wong, Dez Reed}
	{Keywords: continuation, ntinuation, control flow, programming languages}
	{SIGBOVIK_2020_paper_33}
	{hbc: A celebration of undefined behavior}
	{Andrew Benson}
	{Keywords: compilers, undefined behavior, Bash misuse, computer music, Principles of Imperative Computation}
	{SIGBOVIK_2020_paper_34}
	{Learning to be wrong via gradient ascent: A broken clock is right twice a day, but a clock that runs backwards can be used to tell the time!}
	{Alex Meiburg}
	{Keywords: machine learning, gradient descent, loss landscape, logistic regression, biased estimators, eliminating bias, overtraining}
	{SIGBOVIK_2020_paper_35}
	{A thorough investigation of the degree to which the COVID-19 pandemic has enabled subpar-quality papers to make it into the proceedings of SIGBOVIK, by reducing the supply of authors willing to invest the necessary effort to produce high-quality papers}
	{Shalin Shah}
	{Keywords: COVID-19, SIGBOVIK, lazy, quality, sadness, big Oof}
	{SIGBOVIK_2020_paper_36}
	{The Pacman effect and the Disc-Sphere Duality}
	{Francisco Ferreira, Fulvio Gesmundo, Lorenzo Gheri, Pietro Gheri, Riccardo Pietracaprina, Fangyi Zhou}
	{Keywords: Pacman, peace, Earth, flat, round, disc, sphere}
	{SIGBOVIK_2020_paper_37}
	{State-of-the-Art Reviewing: A radical proposal to improve scientific publication}
	{Samuel Albanie, Jaime Thewmore, Robert McCraith, Jo\~ao F.\@ Henriques}
	{Keywords: peer review, SotA, State-of-the-Art, computer vision, machine learning}
	{SIGBOVIK_2020_paper_38}

% TODO
\addreview{SIGBOVIK_2020_review_3}{0cm}
\addreview{SIGBOVIK_2020_review_4}{0cm}
\addreview{SIGBOVIK_2020_review_6}{0cm}
\addreview{SIGBOVIK_2020_review_9}{0cm}
\addreview{SIGBOVIK_2020_review_10}{0cm}
\addreview{SIGBOVIK_2020_review_11}{0cm}
\addreview{SIGBOVIK_2020_review_12}{0cm}
